---
title: "W201 Portfolio"
author: "Jessica Matthews"
date: "MIDS Spring 2018"
site: bookdown::bookdown_site
documentclass: book
bibliography: references.bib
link-citations: yes
biblio-style: apalike
---

<!-- This won't be displayed but it will initialize your R session. Add any R libraries you need here. -->
```{r init,include=FALSE,echo=FALSE}
library(magrittr)
readLines("https://www.zotero.org/api/users/4665557/items/top?limit=25&format=bibtex&key=51JmbR0knlGWsDlgBfissJ7C&v=1")%>%
writeLines("references.bib")
```


# Welcome! {-}

<!-- You can include images saved within your repo... -->

<!-- Below this line is just examples of how you can embed video from Google Drive. First you have to enable sharing, then just get the object ID which is that long string between d/ and /preview and will also be appended to any sharing link you generate for your video. -->
<p>
```{r hello-benji,echo=FALSE,fig.cap='Big Hello from Jess',fig.align='center'}
knitr::include_url('https://drive.google.com/file/d/1bYicXPttYuI8Pu4KDQvpQE6me4MOoSxu/preview')
```


### Abstract of speed reading {-}

Natural Language Processing can be used to quickly understand industry trends from annual reports.  
Annual reports are often hundreds of pages long and that information 
is rarely compared in a systematic way.  That qualitative information can identify strategy changes before they show up in earnings reports.  


### Abstract of sales prep dashboard {-}

This idea is based on the observation that B2B sales people who do back ground research to understand their customer's business are more successful.  Reducing the amount of time it takes sales people to do that research, but automating the prep can improve productivity and the quality of preparation.  This idea begins to envision a tool to automate sales preparation to support the sale of research and advisory services to HR executives. 


## About the author {-}

I am a product manager at Gartner based in San Francisco.  I am originally from Pennsylvania where I received my BA and MA in Telecommunications Studies at Penn State.  When not working or studying data science, I enjoy performing improv and seeing live music.   

*Updated: `r Sys.Date()`*
